ChIP-seq example

### 2018-11-07 analysis/chipseq.Rmd
wflow_publish("chipseq.Rmd")

Set up environment
------------------

We begin by loading the smashr, ggplot2 and cowplot packages, as well
as some additional functions used to implement the analysis below.

@@

The ChIP-seq data are sequencing read counts for transcription
factor YY1 in cell line GM12878, restricted to 880,001--1,011,072 bp
on chromosome 1. These data were collected as part of the ENCODE
("Encyclopedia Of DNA Elements") project.

>>>>

Finally, install the smashr package from GitHub:

```{r install-pkgs-2, eval=FALSE}
devtools::install_github("stephenslab/smashr",upgrade_dependencies = FALSE)
```

See the "Session Info" at the bottom for the versions of the software
and R packages that were used to generate the results shown below.

Set up R environment
--------------------

Loading the smashr, ggplot2 and cowplot packages, as well as some
additional functions used to implement the analysis below.

@@

The ChIP-seq data are sequencing read counts for transcription factor
YY1 in cell line GM12878, restricted to 880,001--1,011,072 bp on
chromosome 1. These data were collected as part of the ENCODE
("Encyclopedia Of DNA Elements") project. The data are included with
the [git repository][smash-github].
